Preliminary Draft

### 2021-07-28 article/draft.tex
some comments in YT subsection about recommendations
updates - discussion

@@

@@

{\bf Lack of misinformation specific interventions.} It is likely that most interventions related to misinformation correspond to interventions that were designed for other policy areas. To illustrate, YouTube explicitly states that: {\it Several policies in our Community Guidelines are directly applicable to misinformation}; such as deceptive practices, impersonation and hate speech policy.

@@

		\item Networked public square / private companies / regulations...

@@

		\item Make point about ``recycling" existing policies (e.g. to tackle terrorism) and apply it to misinformation+

		\item Make point that platforms when they take actions regarding misinformation, they rarely cite misinformation as the reason. E.g. beauty of life, coordinated inauthentic behavior. \href{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}

		\item ``All four Pages have been unpublished for repeated violations of Community Standards and accumulating too many strikes. While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address by demoting links marked wrong by fact checkers and suggesting additional content, none of the violations that spurred today’s removals were related to this." \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{Newsroom}.

		\item YouTube page that says, misinformation falls under other categories existing in the guidelines.

		\item User side: psychological effects (Pennycook, etc.), multi-platforms, indirect effects, strategies... business model

>>>>

{\color{red} explain experiment + make it only about health and add exact number (e.g. 45 health videos, 10 545 recommendations) .}

@@

{\color{red} Channel level ! }

@@

{\bf Lack of misinformation specific interventions.} It is likely that most interventions related to misinformation correspond to interventions that were designed for other policy areas or aim violations that fall into other categories cited in the platforms' guidelines. To illustrate, YouTube explicitly states\footnote{See {\it What policies exist to fight misinformation on Youtube?} \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}{youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}.} that: {\it Several policies in our Community Guidelines are directly applicable to misinformation}; such as deceptive practices, impersonation and hate speech policy. Similarly, Facebook took down four pages related to InfoWars and cited as a reason the repeated violations of Community Standards and not false news.\footnote{An article published \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{on Facebook Newsroom (2018)} states that : ``All four Pages have been unpublished for repeated violations of Community Standards and accumulating too many strikes. While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address by demoting links marked wrong by fact checkers and suggesting additional content, none of the violations that spurred today’s removals were related to this''.}

Naturally, the design of an intervention by a given online platform in order to moderate content should be adapted to the aimed policy area. Therefor, $classic$ interventions such as account suspension and content deletion, might be efficient for policy areas such as Adult Nudity \& Sexual Activity or Hate Speech. Nevertheless, tackling online misinformation is an active area of research and interventions specifically designed for this $new$ policy area, might be required to avoid undesired effects. Namely, account suspensions may have generated a movement of platform migration towards new alternative social media platforms, with little or no content moderation. We invite the reader to see Rogers (2020)~\cite{rogers2020} for an excellent overview about de-platforming and see Robins-Early (2019)~\cite{huffpost} for a news article about Alex Jones's account suspension on Facebook.

@@

		\item Networked public square / private companies / regulations / coordination...

@@

		\item Make point that platforms when they take actions regarding misinformation, they rarely cite misinformation as the reason. E.g. beauty of life, coordinated inauthentic behavior. %\href{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}

		%\item ``All four Pages have been unpublished for repeated violations of Community Standards and accumulating too many strikes. While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address by demoting links marked wrong by fact checkers and suggesting additional content, none of the violations that spurred today’s removals were related to this." \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{Newsroom}.

		%\item YouTube page that says, misinformation falls under other categories existing in the guidelines.
